RJObject Manual

### 2015-12-07 Documents/manual.tex
Compiling
Specifying models

>>>>

\section{Compiling}
If you have all the dependencies, and have all the paths set up correctly as
specified above, you should be able to compile RJObject by going into the
root RJObject directory and invoking {\tt make}. Alternatively you can follow
the {\tt cmake} instructions in the README.

\section{Specifying models}
When using RJObject, you're really using DNest3. So to implement a model, you
need to write a DNest3 model class and specify the fromPrior, perturb,
logLikelihood methods etc. All RJObject provides is a quick and relatively
painless way of incorporating a trans-dimensional object into your model and
specifying heirarchical priors for its parameters. For example, consider
the SineWave example from the RJObject paper. There are an unknown number of
sinusoids $N$, and each of the sinusoids has an unknown period $T_i$, amplitude
$A_i$, and phase $\phi_i$. To use DNest3 on this problem, you'd have to write
the fromPrior and perturb methods for all of these parameters, which is
potentially very annoying.
